Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-06-20 paper1.tex
add sql

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
%\usepackage{epsf}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}	% Extra extra math symbols
\usepackage{natbib}
%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{etoolbox}

@@

We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}. The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.

>>>>

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
%\usepackage{epsf}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}	% Extra extra math symbols
\usepackage{natbib}
%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{etoolbox}
\usepackage{listings}

@@

We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}. The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0. The following SQL query selects the cluster halos:
\begin{lstlisting}[language=SQL]
SELECT * 
FROM   mfield..fof 
WHERE  snapnum IN (SELECT snapnum 
                   FROM   snapshots..mr 
                   WHERE  z BETWEEN 0.01 AND 0.5) 
       AND m_crit200 > 100 
       AND random BETWEEN 0 AND 10000 
\end{lstlisting}
To select the corresponding galaxies, we use:
\begin{lstlisting}[language=SQL, breaklines=true]
SELECT sh.fofid, 
       sh.subhaloid, 
       g.galaxyid, 
       g.x, 
       g.y, 
       g.z, 
       g.redshift, 
       g.velx, 
       g.vely, 
       g.velz, 
       sdss.g_sdss, 
       sdss.r_sdss, 
       sdss.i_sdss 
FROM   mfield..fofsubhalo AS sh 
       INNER JOIN mpagalaxies..delucia2006a AS g 
               ON sh.subhaloid = g.subhaloid 
       INNER JOIN mpagalaxies..delucia2006a_sdss2mass AS sdss 
               ON g.galaxyid = sdss.galaxyid 
WHERE  sh.fofid IN (SELECT fofid 
                FROM   mfield..fof 
                WHERE  snapnum IN (SELECT snapnum 
                               FROM   snapshots..mr 
                               WHERE  z BETWEEN 0.01 AND 0.5) 
                       AND m_crit200 > 1000 
                       AND random BETWEEN 0 AND 10000) 
\end{lstlisting}
